Data preparation

### 2024-02-26 procesamiento/01-prod_prep-micro.Rmd
update

@@

df1$class10spof <- as_labelled(df1$class10spof)
sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse"

frq(df1$class10spof)
#if NA in class of respondent, replace with spouse

@@

sjlabelled::set_label(df1$class3) <- "Social Class"
frq(df1$class3)

# Class Scheme 5 classes
df1$class5 <- car::recode(
  df1$class11d,
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$class5) <- "Social Class"
#frq(df1$class5)

@@

# Class only R's --------------------------------------------------------------
df1$class10

# Class Scheme 3 classes
df1$class3res <- car::recode(as.numeric(df1$class10),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$class3res) <- "Social Class (R's)"
# frq(df1$class3res)

# Class Scheme 5 classes
df1$class5res <- car::recode(
  as.numeric(df1$class10),
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$class5res) <- "Social Class (R's)"
# frq(df1$class5res)

# Class Scheme 6 classes
df1$class6res <- car::recode(
  as.numeric(df1$class10),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$class6res) <- "Social Class (R's)"
frq(df1$class6res)
# Class only Spouse --------------------------------------------------------------
df1$class10spo

# Class Scheme 3 classes
df1$class3spo <- car::recode(as.numeric(df1$class10spo),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$class3spo) <- "Social Class (Spouse)"
frq(df1$class3spo)

# Class Scheme 5 classes
df1$class5spo <- car::recode(
  as.numeric(df1$class10spo),
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$class5spo) <- "Social Class (Spouse)"
# frq(df1$class5res)

# Class Scheme 6 classes
df1$class6spo <- car::recode(
  as.numeric(df1$class10spo),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)
sjlabelled::set_label(df1$class6spo) <- "Social Class (Spouse)"
```

@@

df1$digclass10f <- factor(df1$digclass10f,
                       levels = c("higher controllers","lo controllers",
                                 "routine nonmanual",
                                 "sempl with emp","sempl without empl","selfempl farm",
                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))

df1$digclass10f <- as_labelled(df1$digclass10f)
sjlabelled::set_label(df1$digclass10f) <- "Social Class - respondent"
frq(df1$digclass10f)

df1$digclass10spof <- as_factor(df1$digclass10spo)
frq(df1$digclass10spof)

@@

# Replace the highest class by dominance criteria 
# Keep the highest of two values:
df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
                     df1$digclass10spof,#social class spouse
                     na.rm = T) # if NA, do nothing
frq(df1$digclass11d)
df1$digclass11d <- 
  sjlabelled::set_labels(df1$digclass11d,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
sjlabelled::set_label(df1$digclass11d) <- "Social Class"
frq(df1$digclass11d)

@@

sjlabelled::set_label(df1$digclass3) <- "Social Class"
frq(df1$digclass3)

# Class Scheme 5 classes
df1$digclass5 <- car::recode(
  df1$digclass11d,
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$digclass5) <- "Social Class"
frq(df1$digclass5)
# Class Scheme 6 classes
df1$digclass6 <- car::recode(
  df1$digclass11d,
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

# Class only R's --------------------------------------------------------------
df1$digclass10

# Class Scheme 3 classes
df1$digclass3res <- car::recode(as.numeric(df1$digclass10),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$digclass3res) <- "Social Class (R's)"
# frq(df1$class3res)

# Class Scheme 5 classes
df1$digclass5res <- car::recode(
  as.numeric(df1$digclass10),
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$digclass5res) <- "Social Class (R's)"
# frq(df1$class5res)

@@

sjlabelled::set_label(df1$digclass6res) <- "Social Class (R's)"
frq(df1$digclass6res)
# Class only Spouse --------------------------------------------------------------
df1$digclass10spo

# Class Scheme 3 classes
df1$digclass3spo <- car::recode(as.numeric(df1$digclass10spo),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$digclass3spo) <- "Social Class (Spouse)"
frq(df1$digclass3spo)

# Class Scheme 5 classes
df1$digclass5spo <- car::recode(
  as.numeric(df1$digclass10spo),
  as.factor = T,
  levels = c(
    'Service class (I+II)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1:2='Service class (I+II)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$digclass5spo) <- "Social Class (Spouse)"
# frq(df1$class5res)

# Class Scheme 6 classes
df1$digclass6spo <- car::recode(
  as.numeric(df1$digclass10spo),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)
sjlabelled::set_label(df1$digclass6spo) <- "Social Class (Spouse)"
```

@@

```{r digclass-egp}
# install.packages("devtools")
# devtools::install_git("https://code.europa.eu/digclass/digclass.git")
library("DIGCLASS")
library(dplyr)

@@

@@

df1$dclass11d <- 
  sjlabelled::set_labels(df1$dclass11d,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
frq(df1$dclass11d)
sjlabelled::set_label(df1$dclass11d) <- "Social Class"

# Class Scheme 3 classes
df1$dclass3 <- car::recode(df1$dclass11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$dclass3) <- "Social Class"
frq(df1$dclass3)
frq(df1$class3)
frq(df1$digclass3)
```

```{r oesch-class}
df1 <- df1 %>% 
  mutate(oesch16 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 16,to_factor = T,label=T),
         oesch8 = isco88_to_oesch(isco88r, self_employed, n_employees, n_classes = 8,to_factor = T,label=T))

df1 <- df1 %>% 
  mutate(oesch16spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 16,to_factor = T,label=T),
         oesch8spo = isco88_to_oesch(isco88spo, self_employed_spo, n_employees_spo, n_classes = 8,to_factor = T,label=T))

# Traditional Upper-middle class
#  [1] "'Large employers'"
#  [2] "'Self-employed professionals'"
# 
# Salaried middle class
#  [9] "'Higher-grade managers and administrators'"
# [10] "'Lower-grade managers and administrators'"

#  [5] "'Technical experts'"
#  [6] "'Technicians'"
# 
# [13] "'Socio-cultural professionals'"
# [14] "'Socio-cultural semi-professionals'"

# # Lower-middle class
#  [3] "'Small business owners with employees'"
#  [4] "'Small business owners without employees'"
# [11] "'Skilled clerks'"
# 
# # Working class
#  [7] "'Skilled manual'"
#  [8] "'Low-skilled manual'"
# 
# [12] "'Unskilled clerks'"
# [15] "'Skilled service'"
# [16] "'Low-skilled service'"

# reorder Oesch's scheme in a (semi)hierarchical order
oesch_hierar <- 
c("'Large employers'","'Self-employed professionals'",
  "'Higher-grade managers and administrators'",
  "'Lower-grade managers and administrators'",
  "'Technical experts'","'Technicians'",
  "'Socio-cultural professionals'","'Socio-cultural semi-professionals'",
  "'Small business owners with employees'","'Small business owners without employees'","'Skilled clerks'",
  "'Skilled manual'","'Skilled service'",
  "'Low-skilled service'","'Unskilled clerks'","'Low-skilled manual'")

# Respondent social class ------------------------------------------------------
df1$oesch16 <- factor(df1$oesch16,
                      levels = oesch_hierar)
frq(df1$oesch16)

# Partner social class ---------------------------------------------------------
df1$oesch16spo <- factor(df1$oesch16spo,
                      levels = oesch_hierar)
frq(df1$oesch16spo)

#   Given that the Oesch's Scheme consider the vertical (skills) and horizontal (work-logic) as the main distinction between classes
# I will colapse in 4 classes that allow to distinguish between hierarchical differences

# 1. Traditional Upper-middle class
# 2. Salaried middle-class
# 3. Lower middle class
# 4. Working Class

df1$oesch4 <- NA
df1$oesch4[df1$oesch16 %in%c("'Large employers'","'Self-employed professionals'")] <- 4
df1$oesch4[df1$oesch16 %in%c("'Higher-grade managers and administrators'",
                             "'Lower-grade managers and administrators'",
                             "'Technical experts'","'Technicians'",
                             "'Socio-cultural professionals'",
                             "'Socio-cultural semi-professionals'")] <- 3
df1$oesch4[df1$oesch16 %in%c( "'Small business owners with employees'",
                              "'Small business owners without employees'",
                              "'Skilled clerks'")] <- 2

df1$oesch4[df1$oesch16 %in%c("'Low-skilled service'",
                             "'Unskilled clerks'",
                             "'Low-skilled manual'")] <- 1

frq(df1$oesch4) # higher number is the hierarchical order of the four main classes

df1$oesch4spo <- NA
df1$oesch4spo[df1$oesch16spo %in%c("'Large employers'","'Self-employed professionals'")] <- 4
df1$oesch4spo[df1$oesch16spo %in%c("'Higher-grade managers and administrators'",
                             "'Lower-grade managers and administrators'",
                             "'Technical experts'","'Technicians'",
                             "'Socio-cultural professionals'",
                             "'Socio-cultural semi-professionals'")] <- 3
df1$oesch4spo[df1$oesch16spo %in%c( "'Small business owners with employees'",
                              "'Small business owners without employees'",
                              "'Skilled clerks'")] <- 2

df1$oesch4spo[df1$oesch16spo %in%c("'Low-skilled service'",
                             "'Unskilled clerks'",
                             "'Low-skilled manual'")] <- 1
frq(df1$oesch4spo)
#if NA in class of respondent, replace with spouse
df1$oesch4_dom  <- ifelse(is.na(df1$oesch4),df1$oesch4spo,df1$oesch4)
frq(df1$oesch4_dom)
# if NA in respondents it is assumed to be lower than spouse
# now, with the cases in we have information for respondent and spouse
# we replace the value by the highest one

# Replace the highest class by dominance criteria 
# Keep the highest of two values:
df1$oesch4_dom <- pmax(df1$oesch4, #social class respondent
                       df1$oesch4spo,#social class spouse
                       na.rm = T) # if NA, do nothing
frq(df1$oesch4_dom)
df1$oesch4_dom <- as_numeric(df1$oesch4_dom)
frq(df1$oesch4_dom)

>>>>

# Trust

```{r}
# sjmisc::frq(df1$v35)
df1$socialtrust <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
df1$socialtrust <- set_na(df1$socialtrust,na = c(0,8,9))
df1$socialtrust <- sjmisc::rec(x = df1$socialtrust,rec = "rev")
# sjmisc::frq(df1$socialtrust)
# hist.default(df1$socialtrust)
```

@@

df1$class10spof <- as_labelled(df1$class10spof)
sjlabelled::set_label(df1$class10spof) <- "Social Class - spouse";frq(df1$class10spof)
#if NA in class of respondent, replace with spouse

@@

sjlabelled::set_label(df1$class3) <- "Social Class Dominance (isko - v1 - V to Intermediate)";frq(df1$class3)

df1$class3_V <- car::recode(df1$class11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$class3_V) <- "Social Class Dominance (isko - v1 - V to Working Class)";frq(df1$class3_V)

@@

# Class only R's --------------------------------------------------------------
# Class Scheme 3 classes
df1$class3res <- car::recode(as.numeric(df1$class10f),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$class3res) <- "Social Class 3 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class3res)

df1$class3res_V <- car::recode(as.numeric(df1$class10f),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$class3res_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3res_V)

# Class Scheme 6 classes
df1$class6res <- car::recode(
  as.numeric(df1$class10f),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$class6res) <- "Social Class 6 (R's) - (isko - v1 -  V to Intermediate)";frq(df1$class6res)
# Class only Spouse --------------------------------------------------------------

# Class Scheme 3 classes
df1$class3spo <- car::recode(as.numeric(df1$class10spof),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:10='Working Class (VI+VII)'")

sjlabelled::set_label(df1$class3spo) <- "Social Class 3 (Spouse) - (isko - v1 -  V to Intermediate)";frq(df1$class3spo)

df1$class3spo_V <- car::recode(as.numeric(df1$class10spof),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:10='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$class3spo_V) <- "Social Class 3 (R's) - (isko - v1 -  V to Working)";frq(df1$class3spo_V)

# Class Scheme 6 classes
df1$class6spo <- car::recode(
  as.numeric(df1$class10spo),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)
sjlabelled::set_label(df1$class6spo) <- "Social Class 6 (Spouse) - (isko - v1)";frq(df1$class6spo) 
```

@@

df1$digclass10f <- factor(df1$digclass10f,
                       levels = c("higher controllers","lo controllers",
                                 "routine nonmanual",
                                 "sempl with emp","sempl without empl","selfempl farm",
                                 "manual supervisor","skilled manual","semi-unskilld manual","farm labor"),
                       labels = c("I", "II", "IIIab", "IVa", "IVb", "IVc", "V", "VI", "VIIa", "VIIb"))
df1$digclass10f <- as_labelled(df1$digclass10f)
sjlabelled::set_label(df1$digclass10f) <- "Social Class - respondent"
frq(df1$digclass10f)
df1$digclass10spof <- as_factor(df1$digclass10spo)
frq(df1$digclass10spof)

@@

# Replace the highest class by dominance criteria 
# Keep the highest of two values:
df1$digclass11d <- pmax(df1$digclass11, #social class respondent + spouse vs:
                     df1$digclass10spof,#social class spouse
                     na.rm = T) # if NA, do nothing
frq(df1$digclass11d)
df1$digclass11d <- 
  sjlabelled::set_labels(df1$digclass11d,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
                         labels =  c("I", "II", "IIIab", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb")) 
sjlabelled::set_label(df1$digclass11d) <- "Social Class 11 (isko - v2)"
frq(df1$digclass11d)

@@

sjlabelled::set_label(df1$digclass3) <- "Social Class 3 (isko - v2 - V to Intermediate) ";frq(df1$digclass3)

df1$digclass3_V <- car::recode(df1$digclass11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$digclass3_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3_V)

# Class only R's --------------------------------------------------------------
# Class Scheme 3 classes
df1$digclass3res <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$digclass3res) <- "Social Class 3 (R's) - (V to Intermediate - isko - v2)";frq(df1$digclass3res)

df1$digclass3res_V <- car::recode(as.numeric(df1$digclass10f),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$digclass3res_V) <- "Social Class 3 (V to Working Class - isko - v2)";frq(df1$digclass3res_V)

@@

sjlabelled::set_label(df1$digclass6res) <- "Social Class 6 (R's) - (isko - v2)"

# Class only Spouse --------------------------------------------------------------
# Class Scheme 3 classes
df1$digclass3spo <- car::recode(as.numeric(df1$digclass10spo),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV+V)';
                             8:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$digclass3spo) <- "Social Class 3 (Spouse) - (V to Intermediate - isko - v2)";frq(df1$digclass3spo)

df1$digclass3spo_V <- car::recode(as.numeric(df1$digclass10spof),as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:6='Intermediate class (III+IV)';
                             7:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$digclass3spo_V) <- "Social Class 3 (Spouse) (V to Working Class - isko - v2)";frq(df1$digclass3spo_V)

# Class Scheme 6 classes
df1$digclass6spo <- car::recode(
  as.numeric(df1$digclass10spo),
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)
sjlabelled::set_label(df1$digclass6spo) <- "Social Class  6 (Spouse) - (isko - v2)"
```

@@

```{r digclass-egp}
# install.packages("devtools") 
# devtools::install_git("https://code.europa.eu/digclass/digclass.git")

library("DIGCLASS")
library(dplyr)

@@

#0.1 label respondent egp11 classes
df1$egp11 <- 
  sjlabelled::set_labels(df1$egp11,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb"))

#0.2 label spouse egp11 classes
df1$egp11spo <- 
  sjlabelled::set_labels(df1$egp11spo,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb"))

@@

df1$dclass11d <- 
  sjlabelled::set_labels(df1$dclass11d,
                         levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10,11),
                         labels =  c("I", "II", "IIIa","IIIb", "IVa", "IVb", 
                                     "IVc", "V", "VI", "VIIa", "VIIb"))

sjlabelled::set_label(df1$dclass11d) <- "Social Class 11 Dominance (EGP11 -  DIGICLASS)";frq(df1$dclass11d)

# Class scheme using dominance-------------------------------------------------
# # Class Scheme 3 classes -  V to intermediate class
df1$dclass3 <- car::recode(df1$dclass11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV+V)',
                                      'Working Class (VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:8='Intermediate class (III+IV+V)';
                             9:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$dclass3) <- "Social Class 3 Dominance (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3)

# Class Scheme 3 classes -  V to working class
df1$dclass3_V <- car::recode(df1$dclass11d,as.factor = T,
                            levels =c('Service Class (I+II)',
                                      'Intermediate class (III+IV)',
                                      'Working Class (V+VI+VII)'), 
                            "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV)';
                             8:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$dclass3_V) <- "Social Class 3 Dominance (V to Working Class - DIGCLASS)";frq(df1$dclass3_V)

# Class Scheme 3 classes -  IIIb to working class
df1$dclass3_III <- car::recode(df1$dclass11d,as.factor = T,
                            levels =c('Service Class',
                                      'Intermediate class',
                                      'Working Class'), 
                            "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")

sjlabelled::set_label(df1$dclass3_III) <- "Social Class 3 Dominance (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3_III)

# Class Scheme 3 classes -  IIIb and V to working class
df1$dclass3_III_V <- car::recode(df1$dclass11d,as.factor = T,
                            levels =c('Service Class',
                                      'Intermediate class',
                                      'Working Class'), 
                            "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")

sjlabelled::set_label(df1$dclass3_III_V) <- "Social Class 3 Dominance (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3_III)

# Class Scheme 6 classes
df1$dclass6 <- car::recode(
  df1$dclass11d,
  as.factor = T,
  levels = c(
    'Service class (I - higher grade)',
    'Service class (II - lower grade)',
    'Routine non-manual (IIIa+b)',
    'Petty-bourgeoise (IVa+b+c)',
    'Skilled manual workers and supv. (V+VI)',
    'Non-skilled manual workers (VIIa+b)'
  ),
  "1='Service class (I - higher grade)';
   2='Service class (II - lower grade)';
   3:4='Routine non-manual (IIIa+b)';
   5:7='Petty-bourgeoise (IVa+b+c)';
   8:9='Skilled manual workers and supv. (V+VI)';
   10:11='Non-skilled manual workers (VIIa+b)'"
)

sjlabelled::set_label(df1$dclass6) <- "Social Class 6 Dominance (DIGCLASS)"
```

```{r digclass-egp-respondent}
# Class scheme using Respondent-------------------------------------------------
# # Class Scheme 3 classes -  V to intermediate class

df1$dclass3res <- car::recode(df1$egp11,as.factor = T,
                           levels =c('Service Class (I+II)',
                                     'Intermediate class (III+IV+V)',
                                     'Working Class (VI+VII)'), 
                           "1:2='Service Class (I+II)';
                             3:8='Intermediate class (III+IV+V)';
                             9:11='Working Class (VI+VII)'")

sjlabelled::set_label(df1$dclass3res) <- "Social Class 3 (R's) - (V to Intermediate Class-  DIGICLASS)";frq(df1$dclass3res)

# Class Scheme 3 classes -  V to working class
df1$dclass3res_V <- car::recode(df1$egp11,as.factor = T,
                             levels =c('Service Class (I+II)',
                                       'Intermediate class (III+IV)',
                                       'Working Class (V+VI+VII)'), 
                             "1:2='Service Class (I+II)';
                             3:7='Intermediate class (III+IV)';
                             8:11='Working Class (V+VI+VII)'")

sjlabelled::set_label(df1$dclass3res_V) <- "Social Class 3 (R's) - (V to Working Class - DIGCLASS)";frq(df1$dclass3res_V)

# Class Scheme 3 classes -  IIIb to working class
df1$dclass3res_III <- car::recode(df1$egp11,as.factor = T,
                               levels =c('Service Class',
                                         'Intermediate class',
                                         'Working Class'), 
                               "c(1,2)='Service Class';c(3,5,6,7,8)='Intermediate class';c(4,9,10,11)='Working Class'")

sjlabelled::set_label(df1$dclass3res_III) <- "Social Class 3 (R's) - (IIIb to Working Class - DIGCLASS)";frq(df1$dclass3res_III)

# Class Scheme 3 classes -  IIIb and V to working class
df1$dclass3res_III_V <- car::recode(df1$egp11,as.factor = T,
                                 levels =c('Service Class',
                                           'Intermediate class',
                                           'Working Class'), 
                                 "c(1,2)='Service Class';c(3,5,6,7)='Intermediate class';c(4,8,9,10,11)='Working Class'")

sjlabelled::set_label(df1$dclass3res_III_V) <- "Social Class 3 (R's) - (IIIb+V to Working Class - DIGCLASS)";frq(df1$dclass3res_III_V)
```

```{r digclass-egp-spouse}
# Class scheme using Spouse-------------------------------------------------
# # Class Scheme 3 classes -  V to intermediate class
